---
title: "Multiple Regression Cross-Validation"
author: "Max Barshay"
date: "8/19/2021"
output: html_document
---

```{r}
library(coda)
library(rstan)
library(Rcpp)
```

I am loading in the Bayesian Multiple Regression model that was trained on the 25 sites in `Final Multiple Regression.Rmd`.

```{r}
load("/Users/mdbarshay/Documents/GlacialModeling/Final_MR_Results.Rdata")
load("/Users/mdbarshay/Documents/GlacialModeling/Final_MR_Summary.Rdata")
```


```{r}
MB_2015 = read.csv("/Users/mdbarshay/Desktop/FROST/Glaciology_Data_for_Max/mb_by_year/Mass_balance_data-2015.csv")
MB_2015
```


```{r}
mean_xcoord_2015 = mean(MB_2015[,"x.i93"])
sd_xcoord_2015 = sd(MB_2015[,"x.i93"])
mean_ycoord_2015 = mean(MB_2015[,"y.i93"])
sd_ycoord_2015 = sd(MB_2015[,"y.i93"])
mean_elevation_2015 = mean(MB_2015[,"elvev.m.a.s.l."])
sd_elevation_2015 = sd(MB_2015[,"elvev.m.a.s.l."])
```


This contains (x_coord, y_coord, elevation) triplets for almost 500,000 points on and round the glacier. 

```{r}
full_glacier = read.table("/Users/mdbarshay/Desktop/FROST/Glaciology_Data_for_Max/LaJokull-2015-maiWV100x100.dat", sep=" ")
```


If the (x_coord, y_coord) was not on the glacier the elevation was recorded as 1.70141e+38, but for convenience I just convert this to 0. 

```{r}
full_glacier[full_glacier == 1.70141e+38] = 0
```

I now add a pythonically-indexed 'index' column and re-order and re-name the columns.

```{r}
full_glacier[,"index"] = 0:(length(full_glacier[,"V1"]) - 1)
full_glacier = full_glacier[,c(4,1,2,3)]
colnames(full_glacier) = c("index", "x_coord", "y_coord", "elevation")
```

```{r}
zero_rows = full_glacier[,"elevation"] == 0
head(zero_rows)
```

```{r}
subsetted_glacier = full_glacier[!zero_rows,]
```


I have to standardize w.r.t. the 25 data points because that is how I did it in my fitted model.

```{r}
subsetted_glacier[,"x_coord"] = (subsetted_glacier[,"x_coord"] - mean_xcoord_2015) / sd_xcoord_2015
subsetted_glacier[,"y_coord"] = (subsetted_glacier[,"y_coord"] - mean_ycoord_2015) / sd_ycoord_2015
subsetted_glacier[,"elevation"] = (subsetted_glacier[,"elevation"] - mean_elevation_2015) / sd_elevation_2015
```

```{r}
# using cbind so they don't point to same place in memory
standardized_subsetted_glacier = cbind(subsetted_glacier)
standardized_subsetted_glacier
```



```{r}
len = length(standardized_subsetted_glacier[,"index"])
empty = numeric(len)
standardized_subsetted_glacier[,"predictions"] = empty
for (i in 1:len){
  N = length(MR_Results[,"beta0"])
  prediction = MR_Results[, "beta0"] + MR_Results[, "beta1"] * standardized_subsetted_glacier[i,"x_coord"] + MR_Results[, "beta2"] * standardized_subsetted_glacier[i,"y_coord"] + MR_Results[, "beta3"] * standardized_subsetted_glacier[i,"elevation"] + (rt(N, MR_Results[,"nu"]) * MR_Results[,"sigma"])
  standardized_subsetted_glacier[i,"predictions"] = mean(prediction)
}

```


```{r}
write.csv(standardized_subsetted_glacier, file="MR_standardized_subsetted_glacier.csv")
```

```{r}
write.csv(full_glacier, file="full_glacier.csv")
```

